\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage[bookmarks=true,pdfstartview=FitH,bookmarksopen=true]{hyperref}
\usepackage{bookmark}
\usepackage{url}

\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}
\newcommand{\Hrule}{\rule{\linewidth}{0.3mm}}

\makeatletter% since there's an at-sign (@) in the command name
\renewcommand{\@maketitle}{%
  \parindent=0pt% don't indent paragraphs in the title block
  \centering
  {\Large \bfseries{\@title}}
  \HRule\par%
%  \textit{\@author}
  \textit{\@author \hfill \@date \newline}
  \par
}
\makeatother% resets the meaning of the at-sign (@)

\title{Statement of Intent}
\author{Carleton University}\date{M.Eng: Electrical and Computer Engineering}

\begin{document}
  \maketitle % prints the title block

I had a keen interest in computers since my high-school days. I used to repair computers on my own and upgrading it with latest operating system was a fun thing to do for me during those days. I started being interested in programming when I took a Robotics course during my under graduation.\\

After completing my under-graduation, I got selected in a Telecom product development organization as a Software developer from the campus interview. My 1st project was to develop SMS server on the Linux platform. So, I learned about Linux by reading books and watching online tutorials. From that point onward, I have kept on learning about new computer science concepts and technologies by myself. By working on real world projects in a team environment, I have gained valuable skills such as teamwork, planning and project management.\\

I have learned about core computer science subjects such as Algorithms, Database systems, Data structures and Operating systems on my own. I frequently participate in online competitive programming contests on HackerRank to improve my programming skills. Also, I educate myself by taking different online courses on edx, coursera and udacity. I do freelancing in my spare time to apply my skills which i have gained from online courses into the real world projects.\\

I am quite fond of open source software development. I regularly contribute in open source projects hosted on \href{http://www.GitHub.com/mehul-m-prajapati}{GitHub} with other contributors to make an impact in a large community. I attend  technology events organize from \href{www.meetup.com}{meetup.com} to get awareness about latest trends in the market. The renowned groups in which I go are as follows,

\begin{itemize}
   \item \href{https://developers.google.com/groups/chapter/106261089114347152720/}{Google Developer Groups}
   
   \item \href{http://mozillaindia.org/}{Mozilla} 
   
   \item \href{https://www.meetup.com/ahmedabad-wp-meetup/members/72560962/}{Wordpress}
   
   \item \href{https://pythonexpress.in/}{Python Express}
\end{itemize}

I possess a high observation power. Therefore, I adapt to new things very quickly. I like to solve challenging problems. The kind of problems that have not been solved before, that might not even appear to be problems at first sight. The kind of problems one learns to solve at the universities.\\

My career goal is to become a \textbf{Data scientist}. This domain is a combination of mathematics and programming which suits my background and future interests. I am getting familiar with Machine learning by doing online courses and reading online articles on this topic.\\

I have recently developed a deep learning based chatbot leveraging TensorFlow library. This project tries to reproduce the results of a Neural Conversational Model. It uses a RNN (seq2seq model) for sentence predictions. It is done using python and TensorFlow. I participate in competitions hosted on \href{https://www.kaggle.com/}{kaggle} to get hands on exposure.\\

\newpage
My desire to find better and more efficient methods of powering our lives through machine learning products has inspired me to study Carleton’s masters program in Electrical and computer engineering. I have professional work experience, the motivation and the zeal to pursue further education. I believe that University of Carleton’s graduate program would be the best place for me to achieve my future goals.\\

I want to study at the University of Carleton for a number of reasons; first and foremost is that there are highly qualified professors in the university. Secondly, the university offers data science specialization and work-integrated learning opportunities. Lastly, the university provides a chance to participate in the community activities. Thus, I would feel privileged to be a part of Carleton university's graduate program.

  \end{document}