\documentclass{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage[bookmarks=true,pdfstartview=FitH,bookmarksopen=true]{hyperref}
\usepackage{bookmark}
\usepackage{url}

\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}
\newcommand{\Hrule}{\rule{\linewidth}{0.3mm}}

\makeatletter% since there's an at-sign (@) in the command name
\renewcommand{\@maketitle}{%
  \parindent=0pt% don't indent paragraphs in the title block
  \centering
  {\Large \bfseries{\@title}}
  \HRule\par%
%  \textit{\@author}
  \textit{\@author \hfill \@date \newline}
  \par
}
\makeatother% resets the meaning of the at-sign (@)

\title{Statement of Intent}
\author{University of Ottawa}\date{M.Sc Computer Science}

\begin{document}
  \maketitle % prints the title block

By developing computer games, line follower robots and repairing computers, I got overwhelmed with electronics and programming since my high-school days. I started being more interested in programming when I took a Robotics course in college. Therefore, I decided to make a career in the software industry.\\

After completing my under-graduation, I was selected in a product development company as a Software developer from the campus interview. I got the opportunity to work on Linux platform for the first time. So, I learned about Linux by reading books and watching tutorials. From that point onwards, I have kept on learning about new computer science concepts and technologies by myself. By working on real world projects in a team environment, I have gained valuable skills such as teamwork, planning and project management.\\

I have learned about core computer science subjects including Algorithms, Database systems, Data structures and Operating systems on my own. I frequently participate in online competitive programming contests on HackerRank to improve my programming skills. Also, I educate myself by taking different online courses on edx, coursera and udacity. I do freelancing in my spare time to apply my skills which i have gained from online courses into the real world projects.\\

I am quite fond of open source software development. I regularly contribute in open source projects hosted on \href{http://www.GitHub.com/mehul-m-prajapati}{GitHub} with other contributors to make an impact in a large community. I attend technological meet-ups and events organize from \href{www.meetup.com}{meetup.com} to update myself with the latest technologies. The renowned groups in which I go are as follows,

\begin{itemize}
   \item \href{https://developers.google.com/groups/chapter/106261089114347152720/}{Google Developer Groups}
   
   \item \href{http://mozillaindia.org/}{Mozilla} 
   
   \item \href{https://www.meetup.com/ahmedabad-wp-meetup/members/72560962/}{Wordpress}
   
   \item \href{https://pythonexpress.in/}{Python Express}
\end{itemize}

I possess a high observation power. Therefore, I adapt to new things very quickly. I like solving challenging problems. The kind of problems that have not been solved before, that might not even appear to be problems at first sight. The kind of problems one learns to solve at research universities.\\

My research interest lies in \textbf{Machine Learning} because I like the combination of Mathematics and programming. I have recently developed a deep learning based chatbot leveraging TensorFlow library. This project tries to reproduce the results of a Neural Conversational Model. It uses a RNN (seq2seq model) for sentence predictions. It is done using python and TensorFlow. I am developing new skills in machine learning by participating in competitions hosted on \href{https://www.kaggle.com/}{kaggle}.\\

My long term goal is to become a \textbf{Research scientist} who researches and develops machine learning based innovative products. My desire to find better and more efficient methods of powering our lives through machine learning products has inspired me to study computer science. I have the professional work experience, the motivation and the zeal to pursue further education. I believe that University of Ottawa’s masters program in computer science would be the best place for me to achieve my future goals.\\

I want to study at the University of Ottawa for a number of reasons; first and foremost is that there are potential supervisors whose research interests align well with my own. Secondly, the university offers research-enriched education and work-integrated learning opportunities. Lastly, the university provides a chance to participate in the community activities which I am very fond of. Thus, I will feel privileged to be a part of Ottawa university.

  \end{document}